A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-01-28 sections/Metatheory.tex
Simplifies worklist extension (same with proof)

\begin{figure}
\framebox{$\Gm\jExt\Gm'$}
\begin{gather*}
\inferrule*[right=$\mathtt{\jExt\nil}$]
    {~}{\Gm\jExt\Gm}
\qquad
\inferrule*[right=$\mathtt{\jExt solve}$]
    {|A|_\forall = 0 \quad \Gm_L,[A/\al]\Gm_R \jExt \Gm'}{\Gm_L,\al,\Gm_R \jExt \Gm'}
\\
\inferrule*[right=$\mathtt{\jExt \al}$]
    {\Gm_L,\al,\Gm_R \jExt \Gm'}{\Gm_L,\Gm_R \jExt \Gm'}
\qquad
\inferrule*[right=$\mathtt{\jExt inst}$]
    {\Gm_L,\al[1],\al[2],[\al[1]\to\al[2]/\al]\Gm_R \jExt \Gm'}{\Gm_L,\al,\Gm_R \jExt \Gm'}
\end{gather*}
\caption{Worklist Extension}\label{fig:worklist_ext}
\end{figure}

Shown in Figure~\ref{fig:worklist_ext},
worklist extension relates minor changes of worklist during type-checking.
When the algorithm processes the worklist, the first judgment is processed,
and the rest of the worklist roughly remains its shape.
Worklist extension formally defines the minor changes of the shape by three cases:
existential variable solving ($\mathtt{\jExt solve}$), existential variable addition ($\mathtt{\jExt \al}$)
and existential variable instantiation ($\mathtt{\jExt inst}$). \jimmy{Is the 3rd case redundant?}

>>>>

\begin{figure}
\framebox{$\Gm\jExt\Gm'$}
\begin{gather*}
\inferrule*[right=$\mathtt{\jExt\nil}$]
    {~}{\Gm\jExt\Gm}
\qquad
\inferrule*[right=$\mathtt{\jExt solve}$]
    {|A|_\forall = 0 \quad \Gm_L,[A/\al]\Gm_R \jExt \Gm'}{\Gm_L,\al,\Gm_R \jExt \Gm'}
\qquad
\inferrule*[right=$\mathtt{\jExt \al}$]
    {\Gm_L,\al,\Gm_R \jExt \Gm'}{\Gm_L,\Gm_R \jExt \Gm'}
\end{gather*}
\caption{Worklist Extension}\label{fig:worklist_ext}
\end{figure}

Shown in Figure~\ref{fig:worklist_ext},
worklist extension relates minor changes of worklist during type-checking.
When the algorithm processes the worklist, the first judgment is processed,
and the rest of the worklist roughly remains its shape.
Worklist extension formally defines the minor changes of the shape by two cases:
existential variable solving ($\mathtt{\jExt solve}$) and
existential variable addition ($\mathtt{\jExt \al}$).
Existential variable instantiation,
i.e. $\Gm_L,\al,\Gm_R \jExt \Gm_L, \al[1], \al[2], [\al[1] \to \al[2] / \al]\Gm_R$,
can be derived with the combination of the 3 rules.
